% Jakub M. Pawelczak — Curriculum Vitae
% Build: pdflatex cv.tex  (run twice for cross-refs)
% Output filename: 04-2026.pdf  (see build_cv.sh)

\documentclass[11pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.85in]{geometry}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage[hidelinks,breaklinks=true]{hyperref}
\hypersetup{
    pdftitle={Jakub M. Pawelczak — Curriculum Vitae},
    pdfauthor={Jakub M. Pawelczak},
    colorlinks=true,
    urlcolor={black!70},
    linkcolor={black}
}

% ---------- layout ----------
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Section headings: bold, with a thin rule below (no strikethrough)
\titleformat{\section}
  {\normalfont\large\bfseries}
  {}{0pt}{}[{\vspace{0.15em}\titlerule[0.4pt]}]
\titlespacing*{\section}{0pt}{1.0em}{0.35em}

% Two-column entry: date on the left, content on the right
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcommand{\entry}[2]{%
    \begin{tabularx}{\textwidth}{@{}p{1.7in}L@{}}
        {#1} & {#2}
    \end{tabularx}%
    \vspace{0.25em}%
}

% Single-column entry (no date column) — for working papers
\newcommand{\paper}[1]{%
    \noindent #1\par\vspace{0.35em}%
}

% ---------- document ----------
\begin{document}

%% --- HEADER ---
\begin{minipage}[t]{0.6\textwidth}
    {\LARGE\bfseries Jakub M. Pawelczak}\\[0.4em]
    Assistant Professor of Economics\\
    Universidad del Pacífico, Lima, Peru
\end{minipage}%
\hfill
\begin{minipage}[t]{0.38\textwidth}\raggedleft
    \href{mailto:jm.pawelczak@up.edu.pe}{jm.pawelczak@up.edu.pe}\\
    \href{https://www.jakubpawelczak.com}{jakubpawelczak.com}\\[0.2em]
    April 2026
\end{minipage}

\vspace{0.5em}


%% --- APPOINTMENTS ---
\section*{Appointments}
\entry{2025 -- present}{Assistant Professor of Economics, Universidad del Pacífico, Lima, Peru.}


%% --- EDUCATION ---
\section*{Education}
\entry{2025}{%
    Ph.D.\ in Economics, University of Minnesota -- Twin Cities.\newline
    Dissertation: \emph{Essays on Macroeconomics and Housing}.\newline
    Advisor: Prof.\ Christopher Phelan.%
}
\entry{2024}{M.A.\ in Economics, University of Minnesota -- Twin Cities.}
\entry{2018}{M.Sc.\ in Quantitative Economics, Université Paris~1 Panthéon-Sorbonne.}
\entry{2016}{B.S.\ in Mathematics, University of Warsaw.}
\entry{2015}{B.S.\ in Quantitative Methods in Economics and Information Systems, Warsaw School of Economics.}


%% --- FIELDS ---
\section*{Fields of Interest}
Macroeconomics; Housing Markets; Intermediation; Spatial Economics.


%% --- RESEARCH ---
\section*{Working Papers}

\paper{``Flipping Houses in a Decentralized Market.''}

\paper{``Evaluating Universal Government Programs: A Structural Approach with Machine Learning'' (with Filip Premik).}

\paper{``Homeownership as Rental Risk Insurance'' (with Hasan Cetin).}

\paper{``Migration Policy in a Spatial Equilibrium Model'' (with Sean Bassler).}


%% --- CONFERENCES ---
\section*{Conferences}
\entry{2026}{Society for the Advancement of Economic Theory (SAET).}
\entry{2025}{Summer Macro Workshop (Warsaw); Urban Economics Association European Meeting (Berlin); European Economics Congress (Bordeaux).}
\entry{2024}{Korea-America Economic Association (KAEA).}


%% --- TEACHING ---
\section*{Teaching}

\textbf{Universidad del Pacífico}
\vspace{0.25em}

\entry{2026-1}{Macroeconomics~2 (Monetary Economics), Instructor.}

\vspace{0.4em}
\textbf{University of Minnesota -- Twin Cities}
\vspace{0.25em}

\entry{Fall 2024}{International Trade -- Writing Intensive, Instructor.}
\entry{Fall 2023, Spring 2024}{International Trade -- Writing Intensive, Instructor.}
\entry{Summer 2022, 2023, 2024}{Financial Economics, Instructor.}
\entry{Spring 2022}{Intermediate Macroeconomics; Introduction to Econometrics, Teaching Assistant.}
\entry{Fall 2021}{Microeconomic Analysis I/II (Pre-PhD Sequence), Teaching Assistant.}
\entry{Summer 2021}{Math Refresher Course (Graduate), Instructor.}
\entry{Fall 2020, Spring 2021}{Graduate Microeconomic Theory, Teaching Assistant.}


%% --- RESEARCH EXPERIENCE ---
\section*{Research Experience}
\entry{2022 -- 2023}{Research Analyst, Federal Reserve Bank of Minneapolis. RA to Prof.\ Christopher Phelan.}
\entry{2018 -- 2019}{Research Assistant, GRAPE, Warsaw. RA to Prof.\ Marek Weretka (University of Wisconsin -- Madison), ``Normative inference from asset prices'' project, National Science Center grant.}


%% --- HONORS ---
\section*{Honors and Awards}
\entry{2019}{Leonid Hurwicz Fellowship, Department of Economics, University of Minnesota.}
\entry{2018}{Young Economist Competition (3rd place), The Association of Polish Economists.}
\entry{2017 -- 2018}{Scholarship of the French Government (Les Bourses du Gouvernement Français).}
\entry{2016}{QEM Consortium Scholarship.}
\entry{2012}{Scholarship of the Ministry of National Education, Poland.}


%% --- SERVICE ---
\section*{Service}
\entry{2022 -- 2024}{Graduate Student Senator, Student and University Senate, College of Liberal Arts, University of Minnesota (two terms).}


%% --- REFERENCES ---
\section*{References}
\begin{tabularx}{\textwidth}{@{}L L@{}}
Professor Christopher Phelan & Professor V.~V.~Chari \\
University of Minnesota      & University of Minnesota \\
\href{mailto:cphelan@umn.edu}{cphelan@umn.edu} & \href{mailto:chari002@umn.edu}{chari002@umn.edu} \\[0.8em]
Professor Larry E.~Jones     & Professor Jan Werner \\
University of Minnesota      & University of Minnesota \\
\href{mailto:lej@umn.edu}{lej@umn.edu} & \href{mailto:jwerner@umn.edu}{jwerner@umn.edu} \\
\end{tabularx}


%% --- SKILLS ---
\section*{Computer Skills}
Python, R, Stata, MATLAB, \LaTeX, Mathematica.


%% --- LANGUAGES ---
\section*{Languages}
English (fluent), Polish (native), Spanish, German, French (basic).


\end{document}
